On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme

### 2020-11-25 LME-MPM.tex
Nuevos highlights

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Init glossaries
\usepackage[acronym]{glossaries}

\makeglossaries

@@

\setlength{\parskip}{1cm plus 5mm minus 4mm}
%\hline
\setlength{\parskip}{1cm plus 5mm minus 4mm}
\large
\textbf{Highlights}
\normalsize
{\color{blue}
\begin{itemize}
\item A new accurate and efficient time integration scheme for the \acrshort{mpm} is proposed.
\item The \acrfull{lme} approximation technique is a robust substitute of the traditional shape functions within the \acrshort{mpm} framework .
\item The proposed approach might improve large strain fast dynamic \acrshort{mpm} simulations as grid-crossing pathology are clearly mitigated.  
\end{itemize}
}
%\begin{highlights}
%\end{highlights}

@@

\subsubsection{Sensitive analysis to $\widehat{\gamma}$ parameter}
\label{sec:Sensitive-analysis-gamma}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Init glossaries
\usepackage[acronym]{glossaries}
\makeglossaries

@@

\setlength{\parskip}{1cm plus 5mm minus 4mm}
%\hline
\setlength{\parskip}{1cm plus 5mm minus 4mm}
\large
\textbf{Highlights}
\normalsize
{\color{blue}
\begin{itemize}
\item An efficient time integration scheme for the \acrshort{mpm} is proposed.
\item The Local Maximum-Entropy approximants as an alternative of the standard \acrshort{mpm} shape functions.
\item This approach might improve large strain fast dynamic MPM simulations. 
\end{itemize}
}
%\begin{highlights}
%\end{highlights}

@@

\subsubsection{Sensitive analysis to \texorpdfstring{$\widehat{\gamma}$}{gamma}  parameter}
\label{sec:Sensitive-analysis-gamma}
